### 2016-04-22 manuscript-body.tex
Promot subsubsections to subsections

\subsubsection{Misconceptions research in computing education tends to
ignore students' productive
knowledge}\label{misconceptions-research-in-computing-education-tends-to-ignore-students-productive-knowledge}

@@

\subsubsection{Not all cognitive programming bugs imply a problem with
the
student}\label{not-all-cognitive-programming-bugs-imply-a-problem-with-the-student}

@@

\subsubsection{Examples motivate the need for contextual-sensitivity in
modeling programming
cognition}\label{examples-motivate-the-need-for-contextual-sensitivity-in-modeling-programming-cognition}

@@

% \subsubsection{Manifold models of cognition explain context-dependence

>>>>

\subsection{Misconceptions research in computing education tends to
ignore students' productive
knowledge}\label{misconceptions-research-in-computing-education-tends-to-ignore-students-productive-knowledge}

@@

\subsection{Not all cognitive programming bugs imply a problem with
the
student}\label{not-all-cognitive-programming-bugs-imply-a-problem-with-the-student}

@@

\subsection{Examples motivate the need for contextual-sensitivity in
modeling programming
cognition}\label{examples-motivate-the-need-for-contextual-sensitivity-in-modeling-programming-cognition}

@@

% \subsection{Manifold models of cognition explain context-dependence
